Airspace configuration with Monte Carlo tree search

### 2018-01-28 article/prework.tex
(+) added tree policy
(+) new article

@@

>>>>

\subsubsection{Tree policy}
The tree policy includes the selection and the expansion.
\begin{algorithm}
  \caption{Tree policy}
  \begin{algorithmic}
    \Function{TreePolicy}{$v$}
    \While{$v$ is nonterminal}
    \If{$v$ is expandable}
    \Return{\Call{Expand}{$v$}}
    \Else{}{$v \gets$ \Call{BestChild}{$v, C_p$}}
    \EndIf{}
    \EndWhile{}
    \Return{$v$}
    \EndFunction{}
  \end{algorithmic}
\end{algorithm}

@@

\paragraph{Dynamic airspace configuration by genetic
  algorithm\cite{sergeeva2017dynamic}}
The cost function uses five criteria,
\begin{itemize}
  \item imbalance between the workload of the controlled sectors,
  \item the coordination workload,
  \item the number of flight re-entry events,
  \item the number of short transits flight through sectors,
  \item the number of controlled sectors in each airpsace configuration.
\end{itemize}
Only the first one is relevant here, as the neural network gives the workload of
each module.

The airspace is modelled as a graph, the problem boils down to a graph
partitioning problem.

The imbalance is calculated as follow, with \(K_i\) the number of controlled
sectors at time \(t_i\), \(W_{c_{jk}}\) the total workload of all airspace
blocks composing the sector \(k\) at time \(t_i\) and \(c\) the targeted
workload of the sector,
\[
  U_t = \sqrt{%
    \frac{%
      \sum_{k=1}^{K_i} {\left( \frac{|W_{c_{jk}} - c|}{c} \right)}^2
    }{k_i}
  }
\]
